LEGWORK: A python package for computing the evolution and detectability \\ of stellar-origin gravitational-wave sources with space-based detectors

### 2022-01-24 src/ms.tex
different colour for changes

\documentclass[twocolumn]{aastex631}
\received{\today}
\shorttitle{LEGWORK}
\graphicspath{{./}{figures/}}

@@

\newcommand{\todo}[1]{{\color{red}{[TODO: #1}]}}

@@

\subsection{Orbital evolution {\normalfont (\texorpdfstring{\lwModLink{evol}}{evol})}}\label{sec:deriv_evol}
\subsubsection{Circular binaries}
For a circular binary, the orbital evolution due to gravitational-wave emission can be calculated analytically, as the rate at which the separation of the binary shrinks is simply a function of its mass and the current separation \citep[][Eq.~5.6]{Peters+1964}
\begin{equation}{}
    \dv{a}{t}_{e = 0} = -\frac{\beta}{a^3},
\end{equation}
where the constant $\beta$ is defined as
\begin{equation}{\lwFuncURL{utils}{beta}}
    \beta(m_1, m_2) \equiv \frac{64}{5} \frac{G^3}{c^5} m_1 m_2 (m_1 + m_2),
    \label{eq:beta_peters}
\end{equation}
where $c$ is the speed of light, $m_1$ is the primary mass and $m_2$ is the secondary mass. This gives the semi-major axis of a circular binary as a function of time, $t$, as \citep[][Eq.~5.9]{Peters+1964}
\begin{equation}{\lwFuncURL{evol}{evol_circ}}
    a(t, m_1, m_2) = [a_0^4 - 4 t \beta(m_1, m_2)]^{1/4},
    \label{eq:a_over_time_circ}
\end{equation}
where $a_0$ is the initial semi-major axis. Moreover, we can solve for the merger time, the time until the binary will merge, by setting the final semi-major axis in Eq.~\ref{eq:a_over_time_circ}
\begin{equation}{\lwFuncURL{evol}{get_t_merge_circ}}
    t_{\rm merge, circ} = \frac{a_0^4}{4 \beta}.
    \label{eq:t_merge_circular}
\end{equation}

>>>>

\documentclass[twocolumn, linenumbers]{aastex631}
\received{\today}
\shorttitle{LEGWORK}
\graphicspath{{./}{figures/}}

@@

\newcommand{\todo}[1]{{\color{red}{[TODO: #1}]}}
\newcommand{\referee}[1]{{\color{WildStrawberry} #1}}

@@

\subsection{Orbital evolution {\normalfont (\texorpdfstring{\lwModLink{evol}}{evol})}}\label{sec:deriv_evol}
\subsubsection{Circular binaries}
For a circular binary, the orbital evolution due to gravitational-wave emission can be calculated analytically, as the rate at which the separation of the binary shrinks is simply a function of its mass and the current separation \citep[][Eq.~5.6]{Peters+1964}
\begin{equation}{}
    \dv{a}{t}_{e = 0} = -\frac{\beta}{a^3},
\end{equation}
where the constant $\beta$ is defined as
\begin{equation}{\lwFuncURL{utils}{beta}}
    \beta(m_1, m_2) \equiv \frac{64}{5} \frac{G^3}{c^5} m_1 m_2 (m_1 + m_2),
    \label{eq:beta_peters}
\end{equation}
where $c$ is the speed of light, $m_1$ is the primary mass and $m_2$ is the secondary mass. This gives the semi-major axis of a circular binary as a function of time, $t$, as \citep[][Eq.~5.9]{Peters+1964}
\begin{equation}{\lwFuncURL{evol}{evol_circ}}
    a(t, m_1, m_2) = [a_0^4 - 4 t \beta(m_1, m_2)]^{1/4},
    \label{eq:a_over_time_circ}
\end{equation}
where $a_0$ is the initial semi-major axis. Moreover, we can solve for the merger time, the time until the binary will merge, by setting the final semi-major axis in Eq.~\ref{eq:a_over_time_circ} \referee{to zero}.
\begin{equation}{\lwFuncURL{evol}{get_t_merge_circ}}
    t_{\rm merge, circ} = \frac{a_0^4}{4 \beta}.
    \label{eq:t_merge_circular}
\end{equation}
